---
title: "Data QC"
author: "Heath O'Brien"
output:
  tufte::tufte_html: default
  #tufte::tufte_handout: default
---
<!-- see http://rstudio.github.io/tufte/ for info about tufte -->
<!-- type Rscript -e "library(rmarkdown); render('BamQC.rmd')" to knit to html on the server -->
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyr)
library(ggplot2)
library(dplyr)
library(stringr)
library(readr)
library(gridExtra)
library(RColorBrewer)
library(tufte)
rm(list=ls())
source("../Shiny/GENEX-FB1/FormatGGplot.R")
folders <- list.dirs("../Mappings", recursive=FALSE)
folders<-folders[folders!="../Mappings/17193-1"]
folders<-folders[folders!="../Mappings/17193-2"]
LibraryInfo <- read.delim("../Data/SampleInfo.txt", 
                     header=TRUE, stringsAsFactors=TRUE, sep='\t'
                     )
```

# RSeQC
## Mapping Stats
`r margin_note("- rDNA reads not included in first three stats")`
`r margin_note("- # uniquely mapped reads ranges from 57 million to 446 million, with 3 samples (17054, 17160, 15483) having < 100 million")`
`r margin_note("- % rRNA ranges from 0.1% to 56%, with 4 samples (17054, 17160, 18655, 16428) having > 40%")`

``` {r }
#bam_stat.py
RSeQCstats <- data.frame()
for (folder in folders) {
  #print(folder)
  folder=paste(folder, str_extract(folder, '[^/]+$'), sep='/')
  if(file.exists(paste(folder, ".ex.stats.txt", sep=""))){
    temp <- read.delim(paste(folder, ".ex.stats.txt", sep=""), 
                header=FALSE, stringsAsFactors=FALSE, skip=5, sep=':'
                )
    } else {
    temp <- read.delim(paste(folder, ".chr.stats.txt", sep=""), 
                         header=FALSE, stringsAsFactors=FALSE, skip=5, sep=':'
                         )
    }
  temp[4,2] <-strsplit(temp[4,1], ' +')[[1]][4]
  temp[4,1] <- 'Non primary hits'
  temp <- temp[c(6,7,14),]
  temp2 <- read.delim(paste(folder, ".in.stats.txt", sep=""), 
                     header=FALSE, stringsAsFactors=FALSE, skip=5, sep=':'
                     )
  temp2[4,2] <-strsplit(temp[4,1], ' +')[[1]][4]
  temp2[4,1] <- 'Non primary hits'
  temp <-rbind(temp, c("rDNA",sum(as.numeric(temp2[c(6,7),2]))))
  temp[,1] <- c("Multimapped", "Unique", "Paired", "rDNA")
  temp$sample <- tail(strsplit(folder, '/')[[1]], 1)
  RSeQCstats <- rbind(RSeQCstats, temp)
}
RSeQCstats <- spread(RSeQCstats, V1, V2)
#mutate(RSeQCstats, Perc_rDNA = as.numeric(rDNA)/(as.numeric(Unique)+as.numeric(Multimapped)+as.numeric(rDNA))) %>% arrange(Perc_rDNA)
ReadNumbers <- RSeQCstats[,c(1,5)]
RSeQCstats <- RSeQCstats[c(1,5,3,2,4)]
RSeQCstats[,2:5] <- sapply(RSeQCstats[,2:5], function(x) formatC(as.numeric(x), format='d', big.mark=','))
knitr::kable(
  RSeQCstats %>% mutate(sample = str_extract(sample, "^[^-]+")) %>% group_by(sample) %>% summarise_each("sum")
)
write_tsv(RSeQCstats, "../Figures/read_numbers.txt")
```


## Distribution of Reads Among Features (proportion of tags mapping to different feature classes)
`r margin_note("- Intergenic only considers sequence within 10 kb upstream of TSS and downstream of TES")`
`r margin_note("- Exons enriched >10 fold relative to introns")`
`r margin_note("- Introns enriched >10 fold relative to Intergenic")`
`r margin_note("- 1/3rd to 2/3rd of tags map to introns. 2-4% map to intergenic (except for 17198 which is 13% intergenic)")`
`r margin_note("- Number of tags per read ranges from 1.1 to 1.8, except for 17198, which has 0.8")`
`r margin_note("- 17198, also has the highest proportion of intronic and intergenic sequence and the lowest proportion of CDS and second lowest of UTR")`
`r margin_note("- I wonder if this might be an indeciation of DNA contamination?")`


``` {r }
#read_distribution.py
RSeQCdistribution <- data.frame()
ReadNumbers$ExpressedTags = NA
for (folder in folders) {
  #print(folder)
  folder=paste(folder, str_extract(folder, '[^/]+$'), sep='/')
  sample <- tail(strsplit(folder, '/')[[1]], 1)
  temp <- read.delim(paste(folder, ".dist.txt", sep=""), 
                           header=TRUE, stringsAsFactors=FALSE, skip=4, sep=''
                     )
  temp <- temp[-11,]
  tag_total <- sum(temp[c(1,2,3,4,7,10),3])
  ReadNumbers[ReadNumbers$sample == sample,]$ExpressedTags <- sum(temp[c(1,2,3),3])
  temp <- data.frame(V1 = c("Tags_per_read", "CDS", "UTR", "Intron", "Intergenic"), 
                     V2=c(
                  tag_total/as.numeric(ReadNumbers[ReadNumbers$sample == sample,]$Unique),
                  temp[1,3]/tag_total, 
                  sum(as.numeric(temp[c(2,3),3]))/tag_total,
                  temp[4,3]/tag_total,
                  sum(as.numeric(temp[c(7,10),3]))/tag_total
                  )
             )
  temp$sample <- sample
  temp$read_length <- LibraryInfo[LibraryInfo$Sample == str_extract(sample, '^[^-]+'),6]
  RSeQCdistribution <- rbind(RSeQCdistribution, temp)
}
RSeQCdistribution <- spread(RSeQCdistribution, V1, V2)
RSeQCdistribution <- RSeQCdistribution[c(1,5,2,6,4,3)]

knitr::kable(
  RSeQCdistribution %>% mutate(sample = str_extract(sample, "^[^-]+")) %>% group_by(sample, read_length) %>% summarise_each("sum")
)
write_tsv(RSeQCdistribution, "../Figures/read_distribution.txt")

```

## Strand

`r margin_note("- Data consistent with second-strand experiment")`

```{r }
#infer_experiment.py
RSeQCstats <- data.frame()
for (folder in folders) {
  folder=paste(folder, str_extract(folder, '[^/]+$'), sep='/')
  temp <- read.delim(paste(folder, ".expt.txt", sep=""), 
                     skip=3, header=FALSE, sep=':'
                     )
  temp$sample <- tail(strsplit(folder, '/')[[1]], 1)
  temp$V1 <- c("Ambiguous", "First Strand", "Second Strand")
  RSeQCstats <- rbind(RSeQCstats, temp)
}
RSeQCstats <- spread(RSeQCstats, V1, V2)

knitr::kable(
    RSeQCstats %>% mutate(sample = str_extract(sample, "^[^-]+")) %>% group_by(sample) %>% summarise_each("sum")
)
write_tsv(RSeQCstats, "../Figures/read_strand.txt")

```

## Insert Size Distribution

`r margin_note("- Sharp peaks indicate that most fragments are shorter than the read length")`
`r margin_note("- Inner distance pretty consistenly at - 125 for Edinbrugh data, but centered at about -50 for Exeter data")`
`r margin_note("- This indicates that fragment size tends to be around 125-150 bp")`


```{r include=FALSE}
#inner_distance.py
RSeQCstats <- data.frame()
for (folder in folders) {
  folder=paste(folder, str_extract(folder, '[^/]+$'), sep='/')
  #print(folder)
  temp <- read.delim(paste(folder, ".inner_distance_freq.txt", sep=""),
                     header=FALSE
                     )
  sample <- tail(strsplit(folder, '/')[[1]], 1)
  temp$sample <- sample
  temp$read_length <- LibraryInfo[LibraryInfo$Sample == str_extract(sample, '^[^-]+'),6]
  RSeQCstats <- rbind(RSeQCstats, temp)
}
write_tsv(RSeQCstats, "../Figures/read_distance.txt")
```

```{r dev.args = list(bg = 'transparent')}
ggplot(RSeQCstats, aes(x=(V1+V2)/2, y=V3, colour=read_length, group=sample)) +
  geom_line() +
  ylab('reads') +
  xlab('inner distance') +
  scale_colour_brewer(type = "qual", palette = 6) +
  main_theme() +
  theme(legend.position=c(.8,.8))

```

## Splice Junction Saturation

`r margin_note("- It looks like both known and novel splice sites continue to be found")`

```{r include=FALSE}
#junction_saturation.py
RSeQCstats <- data.frame()
for (folder in folders) {
  folder=paste(folder, str_extract(folder, '[^/]+$'), sep='/')
  eval(parse(file = paste(folder, ".junctionSaturation_plot.r", sep=""))[2:5])
  temp<-rbind(
              data.frame(percent_reads=x, junctions=z, Category='All'),
              data.frame(percent_reads=x, junctions=y, Category='Known'),
              data.frame(percent_reads=x, junctions=w, Category='Novel')
              )
  sample <- tail(strsplit(folder, '/')[[1]], 1)
  temp$sample <- sample
  temp$ReadNumbers <- as.numeric(ReadNumbers[ReadNumbers$sample == sample,2])
  temp$read_length <- LibraryInfo[LibraryInfo$Sample == str_extract(sample, '^[^-]+'),6]
  RSeQCstats <- rbind(RSeQCstats, temp)
}
write_tsv(RSeQCstats, "../Figures/junciton_sat.txt")
```

```{r dev.args = list(bg = 'transparent'), warning=FALSE}
ggplot(RSeQCstats, aes(y=junctions, x=ReadNumbers*percent_reads/100, group=sample, colour=read_length)) +
  geom_point() +
  #xlim(c(0,500)) +
  #scale_y_log10() +
  scale_colour_brewer(type = "qual", palette = 6) +
  main_theme() +
  theme(legend.position=c(.8,.9)) +
  facet_wrap(~ Category, scales='free') +
  xlab("Number of Reads")
  ```
  