---
title: "BrainSpan Analysis"
output:
  html_document:
    df_print: paged
---


```{r setup, message=FALSE}
suppressWarnings(library(tidyverse))
library(forcats)
library(ggbiplot)
library(ggdendro)
library(Rtsne)
library(gridExtra)
library(sva)
library(preprocessCore)
source("SARTools/R/FormatGGplot.R")
ggsave2 <- function(...) suppressMessages(ggsave(...))

```

```{r processed_data, results='hide', message=FALSE, cache=TRUE}
#load data
columns_metadata <- read_csv("~/BTSync/FetalRNAseq/Github/GENEX-FB1/Data/BrainSpan/columns_metadata.csv", col_types = cols(
  column_num = col_integer(),
  donor_id = col_integer(),
  donor_name = col_character(),
  age = col_character(),
  gender = col_character(),
  structure_id = col_integer(),
  structure_acronym = col_character(),
  structure_name = col_character()
))

rows_metadata <- read_csv("~/BTSync/FetalRNAseq/Github/GENEX-FB1/Data/BrainSpan/rows_metadata.csv", col_types = cols(
  row_num = col_integer(),
  gene_id = col_integer(),
  ensembl_gene_id = col_character(),
  gene_symbol = col_character(),
  entrez_id = col_integer()
))

# ages are coded as '12 pcw' for prenatal and '12 yrs' for post natal. 
# this separates these into separate columns so 12 year olds aren't lumped in with 12 week old fetuses
# it also combines donor ids with tissue ids to create a unique identifier for each sample
columns_metadata <- columns_metadata %>% separate(age, c('age', 'unit')) %>% 
  mutate(age = as.numeric(age)) %>% 
  mutate(column_name=paste0(donor_id, structure_acronym))

# this uses the unique identifier created above as column names in the expression file
expression <- read_csv("~/BTSync/FetalRNAseq/Github/GENEX-FB1/Data/BrainSpan/expression_matrix.csv", col_names = c('row_number', columns_metadata$column_name))

expression <- expression[,-1] # remove row number column

# filter expression columns and col metadata rows to 12-19 pwc (inclusive)
# by filtering col metadata in parallel, we can continue to use it to create logial vectors to index expression
expression <- expression[, columns_metadata$unit == 'pcw' & findInterval(columns_metadata$age, c(12,19), rightmost.closed=T) == 1]
columns_metadata <- columns_metadata[columns_metadata$unit == 'pcw' & findInterval(columns_metadata$age, c(12,19), rightmost.closed=T) == 1, ]

# combine the various cortex types to reduce the number of labels in plots
columns_metadata <- columns_metadata %>% mutate(structure_recoded=fct_collapse(factor(structure_name),                                                                       cortex=c("dorsolateral prefrontal cortex", 
                                              "ventrolateral prefrontal cortex", 
                                              "primary auditory cortex (core)", 
                                              "primary visual cortex (striate cortex, area V1/17)",                                      "anterior (rostral) cingulate (medial prefrontal) cortex", 
                                              "primary motor-sensory cortex (samples)", 
                                              "primary somatosensory cortex (area S1, areas 3,1,2)", 
                                              "primary motor cortex (area M1, area 4)", 
                                              "posterior (caudal) superior temporal cortex (area 22c)", 
                                              "inferolateral temporal cortex (area TEv, area 20)", 
                                              "posteroventral (inferior) parietal cortex",
                                              "orbital frontal cortex"
                                              )
                                        )
      )

columns_metadata <- columns_metadata %>% select(column_name, everything())
# log transform and transpose expression
# expression+1 is often used to avoid zero counts, but this is a bad idea for RPKM, where non-zero values are often much less than 1
# counts can be filtered by tissue with ```filtered.counts <- counts.trans[columns_metadata$structure_acronym %in% c('CB', 'STC', 'DFC', 'AMY'), ]```
rows_metadata<-rows_metadata[rowSums(expression) !=  0,]
expression<-expression[rowSums(expression) !=  0,]
expression_log <- log2(expression+0.0001)
```

```{r pca, message=FALSE, dependson="processed_data", cache=TRUE}

# Sample IDs must be first column of metadata
pca_to_df <- function(pca, metadata) {
  pca_df <- fortify(pca)
  pca_df$Id <- row.names(pca_df)
  colnames(metadata)[1] <- 'Id'
  pca_df %>% left_join(metadata)
}
pca_prop <- function(pca, index) {
  prp <- pca$sdev^2 * 100 / sum(pca$sdev^2)
  round(prp[index],2)
}

pca = prcomp(t(expression_log))
pca_df <- pca_to_df(pca, columns_metadata)

```

```{r pca_plot, message=FALSE, dependson="pca"}
(p1<-ggplot(pca_df, aes(x=PC1, y=PC2, colour=structure_recoded)) + 
      geom_point() +
      xlab(sprintf("PC1 (%0.1f%% explained var.)", pca_prop(pca, 1))) +
      ylab(sprintf("PC2 (%0.1f%% explained var.)", pca_prop(pca, 2))) +
      fte_theme() +
      theme(aspect.ratio=1, legend.position = 'right', legend.text=element_text(size=6)) +
      ggtitle("PCA"))

(p2<-ggplot(pca_df, aes(x=PC1, y=PC2, colour=donor_name)) + 
      geom_point() +
      xlab(sprintf("PC1 (%0.1f%% explained var.)", pca_prop(pca, 1))) +
      ylab(sprintf("PC2 (%0.1f%% explained var.)", pca_prop(pca, 2))) +
      fte_theme() +
      theme(aspect.ratio=1, legend.position = 'right', legend.text=element_text(size=6)) +
      theme(aspect.ratio=1) +
      ggtitle("PCA, coloured by individual"))


#ggsave2("pca1.png", p1)

#ggsave2("pca2.png", p2)
```

```{r tsne, dependson="processed_data", cache=TRUE}
tsne<-Rtsne::Rtsne(t(expression_log), perplexity=10)
```

```{r tsne_plot, dependson="tsne"}
p1 <- as.data.frame(tsne$Y) %>%
  bind_cols(columns_metadata) %>%
  ggplot(aes(V1, V2, colour=structure_recoded))+geom_point() +
      fte_theme() +
      theme(aspect.ratio=1, legend.position = 'right', legend.text=element_text(size=6)) +
  ggtitle("t-SNE")

p2 <- as.data.frame(tsne$Y) %>%
  bind_cols(columns_metadata) %>%
  ggplot(aes(V1, V2, colour=donor_name))+geom_point() +
      fte_theme() +
      theme(aspect.ratio=1) +
  ggtitle("t-SNE, coloured by individual")

p1
ggsave2("tsne1.png", p1)
p2
ggsave2("tsne2.png", p2)

```

```{r hclust, dependson="processed_data", cache=TRUE}
hc <- hclust(dist(t(expression_log)), method="ward.D")
ddata <- dendro_data(as.dendrogram(hc), type = "rectangle")
ddata$labels <- bind_cols(ddata$labels, columns_metadata)
```

```{r hclust_plot, dependson="hclust"}

plot_categories <-function(columns_metadata, hc, column) {
  #column<-enquo(column)
  columns_metadata <- dplyr::select(columns_metadata, column_name, trait := !!column)
  columns_metadata <- columns_metadata[hc[["order"]],]
  columns_metadata$order<-1:nrow(columns_metadata)
  ggplot(columns_metadata, aes(order, 1, fill = trait)) +
     geom_tile() +
     annotate("text", x=nrow(columns_metadata)/2, y=1, hjust=0.5, label=column) +
     scale_y_continuous(expand=c(0,0)) +
     fte_theme() +
     theme(axis.title=element_blank(),
           axis.ticks=element_blank(),
           axis.text=element_blank(),
           legend.position="none") +
     theme(plot.margin = unit(c(0,0,0,0), "cm"))
  
}

p1 <- ggplot(ddata$segments) + geom_segment(aes(x = x, y = y, xend = xend, yend = yend))+fte_theme()+theme(axis.title=element_blank(), axis.text=element_blank()) + theme(plot.margin = unit(c(0,0.1,0,0.1), "cm"))
row1 <- plot_categories(columns_metadata, hc, 'gender')
row2 <- plot_categories(columns_metadata, hc, 'donor_id')
row3 <- plot_categories(columns_metadata, hc, 'structure_recoded')+theme(legend.position = "bottom", legend.text = element_text(size=6))

gp1<-ggplotGrob(p1)
gp2<-ggplotGrob(row1)
gp3<-ggplotGrob(row2)
gp4<-ggplotGrob(row3)
grid.arrange(gp1, gp2, gp3, gp4, ncol=1,heights=c(1/3, 1/6, 1/6, 1/3))
```

```{r combat_brainspan_pca, message=FALSE, warning=TRUE, cache=TRUE, dependson="processed_data"}
batch <- columns_metadata$donor_name
modcombat = model.matrix(~1, data=select(columns_metadata, structure_recoded, donor_name))
combat_brainspan_res = ComBat(dat=expression, batch=batch, mod=modcombat, par.prior=TRUE, prior.plots=FALSE)

combat_brainspan_pca <- prcomp(t(combat_brainspan_res))
combat_Brainspan_pca_df <- pca_to_df(combat_brainspan_pca, columns_metadata)
```

```{r combat_brainspan_pca_plot, dependson="combat_brainspan_pca"}
(p1<-ggplot(combat_Brainspan_pca_df, aes(x=PC1, y=PC2, colour=structure_recoded)) + 
      geom_point() +
      xlab(sprintf("PC1 (%0.1f%% explained var.)", pca_prop(combat_brainspan_pca, 1))) +
      ylab(sprintf("PC2 (%0.1f%% explained var.)", pca_prop(combat_brainspan_pca, 2))) +
      fte_theme() +
      theme(aspect.ratio=1, legend.position = 'right', legend.text=element_text(size=6)) +
      ggtitle("PCA"))
(p2<-ggplot(combat_Brainspan_pca_df, aes(x=PC1, y=PC2, colour=donor_name)) + 
      geom_point() +
      xlab(sprintf("PC1 (%0.1f%% explained var.)", pca_prop(combat_brainspan_pca, 1))) +
      ylab(sprintf("PC2 (%0.1f%% explained var.)", pca_prop(combat_brainspan_pca, 2))) +
      fte_theme() +
      theme(aspect.ratio=1, legend.position = 'right', legend.text=element_text(size=6)) +
      ggtitle("PCA"))
```

```{r genex_data, results='hide', message=FALSE, cache=TRUE}
#load data
counts_vst <- read_tsv("~/BTSync/FetalRNAseq/Github/GENEX-FB1/Results/Sex_PCW_12_20_FDR_0.1_DESeq_kallistoCounts/tables/counts_vst.txt", trim_ws = TRUE)
combined <- expression_log %>% mutate(Id=rows_metadata$ensembl_gene_id) %>% inner_join(counts_vst)

SampleInfo <- read_tsv("~/BTSync/FetalRNAseq/Github/GENEX-FB1/Data/SampleInfo.txt", 
                       col_types = cols(Sample = col_character()), trim_ws = TRUE)

combined_metadata=SampleInfo %>% select(-RIN, -ReadLength) %>% mutate(source='GENEX') %>% bind_rows(columns_metadata %>% select(Sample=column_name, Sex=gender, PCW=age, structure=structure_recoded, donor=donor_name) %>% mutate(source='BrainSpan', Sex=ifelse(Sex=='M', 'Male', 'Female')))


genex_qn <- normalize.quantiles(as.matrix(select(counts_vst, -Id)),copy=TRUE) %>% as.tibble()
colnames(genex_qn) <- colnames(select(counts_vst, -Id))
expression_qn <- normalize.quantiles(as.matrix(expression_log),copy=TRUE) %>% as.tibble()
colnames(expression_qn) <- colnames(expression_log)
combined_qn <- mutate(genex_qn, Id=counts_vst$Id) %>%
  inner_join(mutate(expression_qn, Id=rows_metadata$ensembl_gene_id))
```

```{r genex_pca, cache=TRUE, dependson="genex_data"}
combined_pca <- prcomp(t(select(combined, -Id)))
combined_pca_df <- pca_to_df(combined_pca, combined_metadata)
```

```{r genex-pca_plot, dependson="genex_pca"}
(p1<-ggplot(combined_pca_df, aes(x=PC1, y=PC2, colour=structure)) + 
      geom_point() +
      xlab(sprintf("PC1 (%0.1f%% explained var.)", pca_prop(combined_pca, 1))) +
      ylab(sprintf("PC2 (%0.1f%% explained var.)", pca_prop(combined_pca, 2))) +
      fte_theme() +
      theme(aspect.ratio=1, legend.position = 'right', legend.text=element_text(size=6)) +
      ggtitle("PCA"))



#ggsave2("pca1.png", p1)

#ggsave2("pca2.png", p2)
```

```{r combat_pca, message=FALSE, warning=TRUE, cache=TRUE, dependson="genex_data"}
batch <- combined_metadata$source
modcombat = model.matrix(~1, data=select(combined_metadata, -structure, -donor))
combat_res = ComBat(dat=select(combined, -Id), batch=batch, mod=modcombat, par.prior=TRUE, prior.plots=FALSE)

combat_pca <- prcomp(t(combat_res))
combat_pca_df <- pca_to_df(combat_pca, combined_metadata)
```

```{r combat_pca_plot, dependson="combat_pca"}
(p1<-ggplot(filter(combat_pca_df, Id != '12834OFC'), aes(x=PC1, y=PC2, colour=donor)) + 
      geom_point() +
      xlab(sprintf("PC1 (%0.1f%% explained var.)", pca_prop(combat_pca, 1))) +
      ylab(sprintf("PC2 (%0.1f%% explained var.)", pca_prop(combat_pca, 2))) +
      fte_theme() +
      theme(aspect.ratio=1, legend.position = 'right', legend.text=element_text(size=6)) +
      ggtitle("PCA"))
```

```{r combat_tsne, dependson="combat_pca", cache=TRUE}
combat_tsne<-Rtsne::Rtsne(t(combat_res), perplexity=10, check_duplicates = FALSE)
```

```{r combat_tsne_plot, message=FALSE, dependson="tsne"}
(p1 <- as.data.frame(combat_tsne$Y) %>%
   mutate(Sample=colnames(combat_res)) %>%
   full_join(combined_metadata) %>%
  ggplot(aes(V1, V2, colour=structure))+geom_point() +
      fte_theme() +
      theme(aspect.ratio=1, legend.position = 'right', legend.text=element_text(size=6)) +
  ggtitle("t-SNE"))

(p2 <- as.data.frame(combat_tsne$Y) %>%
   mutate(Sample=colnames(combat_res)) %>%
   full_join(combined_metadata) %>%
    ggplot(aes(V1, V2, colour=donor))+geom_point() +
      fte_theme() +
      theme(aspect.ratio=1) +
  ggtitle("t-SNE, coloured by individual"))

#ggsave2("tsne1.png", p1)

#ggsave2("tsne2.png", p2)

```


```{r combat_hclust, message=FALSE, cache=TRUE, dependson="processed_data"}
hc <- hclust(dist(t(combat_res)), method="ward.D")
combat_ddata <- dendro_data(as.dendrogram(hc), type = "rectangle")
combat_ddata$labels <- combat_ddata$labels %>% mutate(Sample=colnames(combat_res)) %>%
   full_join(combined_metadata)
```

```{r combat_hclust_plot, dependson="hclust"}


p1 <- ggplot(combat_ddata$segments) + geom_segment(aes(x = x, y = y, xend = xend, yend = yend))+fte_theme()+theme(axis.title=element_blank(), axis.text=element_blank()) + theme(plot.margin = unit(c(0,0.1,0,0.1), "cm"))
row1 <- plot_categories(rename(combined_metadata, column_name=Sample), hc, 'source')
row2 <- plot_categories(rename(combined_metadata, column_name=Sample), hc, 'Sex')
row3 <- plot_categories(rename(combined_metadata, column_name=Sample), hc, 'donor')
row4 <- plot_categories(rename(combined_metadata, column_name=Sample), hc, 'structure')+theme(legend.position = "bottom", legend.text = element_text(size=6))

gp1<-ggplotGrob(p1)
gp2<-ggplotGrob(row1)
gp3<-ggplotGrob(row2)
gp4<-ggplotGrob(row3)
gp5<-ggplotGrob(row4)
grid.arrange(gp1, gp2, gp3, gp4, gp5, ncol=1,heights=c(1/3, 1/9, 1/9, 1/9, 1/3))
```

```{r qn_pca, message=FALSE, warning=TRUE, cache=TRUE, dependson="genex_data"}

batch <- combined_metadata$source
modcombat = model.matrix(~1, data=select(combined_metadata, -structure, -donor))
qn_res = ComBat(dat=select(combined_qn, -Id), batch=batch, mod=modcombat, par.prior=TRUE, prior.plots=FALSE)

qn_pca <- prcomp(t(qn_res))
qn_pca_df <- pca_to_df(qn_pca, combined_metadata)
```

``` {r qn_pca_plot, message=FALSE, warning=TRUE, dependson="qn_pca"}
(p1<-ggplot(qn_pca_df, aes(x=PC1, y=PC2, colour=structure)) + 
      geom_point() +
      xlab(sprintf("PC1 (%0.1f%% explained var.)", pca_prop(qn_pca, 1))) +
      ylab(sprintf("PC2 (%0.1f%% explained var.)", pca_prop(qn_pca, 2))) +
      fte_theme() +
      theme(aspect.ratio=1, legend.position = 'right', legend.text=element_text(size=6)) +
      ggtitle("PCA"))
      
```

```{r qn_hclust, message=FALSE, cache=TRUE, dependson="processed_data"}
hc <- hclust(dist(t(qn_res)), method="ward.D")
qn_ddata <- dendro_data(as.dendrogram(hc), type = "rectangle")
qn_ddata$labels <- qn_ddata$labels %>% mutate(Sample=colnames(qn_res)) %>%
   full_join(combined_metadata)
```

```{r qn_hclust_plot, dependson="hclust"}


p1 <- ggplot(qn_ddata$segments) + geom_segment(aes(x = x, y = y, xend = xend, yend = yend))+fte_theme()+theme(axis.title=element_blank(), axis.text=element_blank()) + theme(plot.margin = unit(c(0,0.1,0,0.1), "cm"))
row1 <- plot_categories(rename(combined_metadata, column_name=Sample), hc, 'source')
row2 <- plot_categories(rename(combined_metadata, column_name=Sample), hc, 'Sex')
row3 <- plot_categories(rename(combined_metadata, column_name=Sample), hc, 'PCW')
row4 <- plot_categories(rename(combined_metadata, column_name=Sample), hc, 'donor')
row5 <- plot_categories(rename(combined_metadata, column_name=Sample), hc, 'structure')+theme(legend.position = "bottom", legend.text = element_text(size=6))

gp1<-ggplotGrob(p1)
gp2<-ggplotGrob(row1)
gp3<-ggplotGrob(row2)
gp4<-ggplotGrob(row3)
gp5<-ggplotGrob(row4)
gp6<-ggplotGrob(row5)
grid.arrange(gp1, gp2, gp3, gp5, gp6, ncol=1,heights=c(1/3, 1/9, 1/9, 1/9, 3/9))

```

```{r qn_tsne, dependson="qn_pca", cache=TRUE}
combat_tsne<-Rtsne::Rtsne(t(combat_res), perplexity=10, check_duplicates = FALSE)
```

```{r qn_tsne_plot, message=FALSE, dependson="qn_tsne"}
(p1 <- as.data.frame(qn_tsne$Y) %>%
   mutate(Sample=colnames(qn_res)) %>%
   full_join(combined_metadata) %>%
  ggplot(aes(V1, V2, colour=structure))+geom_point() +
      fte_theme() +
      theme(aspect.ratio=1, legend.position = 'right', legend.text=element_text(size=6)) +
  ggtitle("t-SNE"))

(p2 <- as.data.frame(qn_tsne$Y) %>%
   mutate(Sample=colnames(qn_res)) %>%
   full_join(combined_metadata) %>%
    ggplot(aes(V1, V2, colour=donor))+geom_point() +
      fte_theme() +
      theme(aspect.ratio=1) +
  ggtitle("t-SNE, coloured by individual"))
```

```{r peer_data, results='hide', message=FALSE, cache=TRUE}
#load data
counts_peer <- read_tsv("~/BTSync/FetalRNAseq/Github/GENEX-FB1/Peer/residuals.txt", trim_ws = TRUE)
peer_qn <- genex_qn <- normalize.quantiles(as.matrix(select(counts_peer, -ID)),copy=TRUE) %>% as.tibble()
colnames(peer_qn) <- paste0(colnames(select(counts_peer, -ID)), '_peer')
combined_peer <- mutate(peer_qn, Id=counts_peer$ID) %>% inner_join(combined_qn)

SampleInfo <- read_tsv("~/BTSync/FetalRNAseq/Github/GENEX-FB1/Data/SampleInfo.txt", 
                       col_types = cols(Sample = col_character()), trim_ws = TRUE)

combined_metadata_peer <- SampleInfo %>% select(-RIN, -ReadLength) %>% mutate(source='GENEXPEER', Sample=paste0(Sample, '_peer')) %>% bind_rows(combined_metadata)
```

```{r peer_pca, message=FALSE, warning=TRUE, cache=TRUE, dependson="peer_data"}

batch <- combined_metadata_peer$source
modcombat = model.matrix(~1, data=select(combined_metadata_peer, -structure, -donor))
peer_combat_res = ComBat(dat=select(combined_peer, -Id), batch=batch, mod=modcombat, par.prior=TRUE, prior.plots=FALSE)

peer_combat_pca <- prcomp(t(peer_combat_res))
peer_combat_pca_df <- pca_to_df(peer_combat_pca, combined_metadata_peer)
```

``` {r peer_pca_plot, message=FALSE, warning=TRUE, dependson="peer_pca"}
(p1<- peer_combat_pca_df %>% mutate(structure=ifelse(is.na(structure), source, as.character(structure))) %>%
  ggplot(aes(x=PC1, y=PC2, colour=structure)) + 
      geom_point() +
      xlab(sprintf("PC1 (%0.1f%% explained var.)", pca_prop(peer_combat_pca, 1))) +
      ylab(sprintf("PC2 (%0.1f%% explained var.)", pca_prop(peer_combat_pca, 2))) +
      fte_theme() +
      theme(aspect.ratio=1, legend.position = 'right', legend.text=element_text(size=6)) +
      scale_colour_manual(values=c(brewer.pal(8, 'Paired')[1:5], 'grey', 'black', brewer.pal(8, 'Paired')[6:8])) +
      ggtitle("PCA"))
ggsave2("peer_pca.png")
```

