---
title: "R Notebook"
output: html_notebook
---


- This uses a couple of interesting methods that will come in handy elsewhere:
    - uses system call to tabix to extract count data from bed file
        - this is wrapped in a function, so it should be fairly easy to reuse elsewhere
    - uses purrr::map2 and purr::map_dbl to run cor.test and extract coefficients in a mutate statement
        - it also susbstitutes NA in cases where counts aren't available for a gene
        - I was able to use purrr::safely to skip errors in the get_counts call, but I had to write a wrapper function around cor.test to deal with inputs from these cases. It would be nice if all of this could be handled in-line in my analysis pipe.
        
```{r}
library(tidyverse)
library(stringr)
bed_file="~/BTSync/FetalRNAseq/Github/GENEX-FB2/Data/expression.bed.gz"


gene_positions <- read_delim("~/BTSync/FetalRNAseq/Github/GENEX-FB2/Data/gene_pos.txt",
"\t", escape_double = FALSE, trim_ws = TRUE) %>%
    mutate(pos=paste0(`#Chr`, ':', start, '-', end)) %>% 
  dplyr::select(ID, pos)

genes <- read_delim("~/BTSync/FetalRNAseq/Github/GENEX-FB2/Data/genes.txt",
"\t", escape_double = FALSE, trim_ws = TRUE)

id<-'ENSG00000128191'

get_counts<-function(id, positions=gene_positions, bed=bed_file) {
  gene_pos <- dplyr::filter(positions, ID==id) %>% `$`('pos')
  stopifnot(length(gene_pos) == 1)
  counts <- system(paste("tabix", bed, gene_pos), intern=TRUE) %>%
    str_subset(id) %>%
    str_split('\t')
  stopifnot(length(counts) == 1)
  as.numeric(counts[[1]][5:length(counts[[1]])])
}


X22q <- read_delim("~/BTSync/FetalRNAseq/Github/GENEX-FB2/Data/22q.txt",
"\t", escape_double = FALSE, trim_ws = TRUE)
ref<-X22q[1,]$`Ensembl ID`
X22q<-X22q[-1,]

my_cor_test <- function(x,y){
  if (is.null(x) || is.null(y)) {
    list(p.value=NA, estimate=NA)
  } else cor.test(x,y)
}

cor_results <- vector("list", length(X22q$`Ensembl ID`))
for (i in seq_along(X22q$`Ensembl ID`)) {
  ref <- X22q$`Ensembl ID`[i]
  gene <- X22q$`Gene`[i]
  print(ref)
  cor_results[[i]] <- X22q %>% mutate(gene1=gene, gene_id1=ref, cor_test=map2(ref, `Ensembl ID`, function(x,y) my_cor_test(safely(get_counts)(x)$result, safely(get_counts)(y)$result)),
                       p=map_dbl(cor_test, 'p.value'), r=map_dbl(cor_test, 'estimate')
                       ) %>% 
  dplyr::select(gene1, gene_id1, gene2=Gene, gene_id2=`Ensembl ID`, r, p) 
}
bind_rows(cor_results) %>% write_tsv("~/BTSync/FetalRNAseq/Github/GENEX-FB2/Data/22q_cor.txt")

```

This should give correlations of each gene with RIN

```{r}
headers <- system(paste('tabix -H', bed_file), intern=TRUE) %>%
    str_split('\t') %>% `[[`(1) %>% `[`(-c(1,2,3,4))


pg_scores <- tibble(Id=headers,
               Full=numeric(length(headers)), 
               `5`=numeric(length(headers)), 
               `3`=numeric(length(headers)), 
               `2`=numeric(length(headers)), 
               `1`=numeric(length(headers)), 
               `05`=numeric(length(headers)),
               `01`=numeric(length(headers)),
               `1e-4`=numeric(length(headers)),
               `1e-6`=numeric(length(headers)),
               `5e-8`=numeric(length(headers))
               )
for (cutoff in colnames(pg_scores)[-1]) {
  pgrs_output <- read_table(paste0("~/BTSync/FetalRNAseq/Github/GENEX-FB2/PGRS/Heath_Nick_FExp_SZ_PGC2plusCLOZUK2_PRS_MAF10pc_noMHC.P", cutoff, ".profile"))
  pg_scores[,cutoff] <- pgrs_output[order(match(pgrs_output$IID, pg_scores$Id)),] %>% 
    `$`(SCORE) %>% 
    `[`(1:length(pg_scores$Id))
}

cut_off_mapping <- tibble(name=c('Full', '5', '3', '2', '1', '05', '01', '1e-4', '1e-6', '5e-8'),
                 Cutoff=c(1, 0.5, 0.3, 0.2, 0.1, 0.05, 0.01, 1e-4, 1e-6, 5e-8))

gather(pg_scores, name, PRS, -Id) %>%
  left_join(cut_off_mapping) %>% 
  ggplot(aes(x=log10(Cutoff), y=PRS, group=Id)) + geom_line() + scale_x_reverse()
```

```{r}
# this version works directly with positions, rather than extracting the position from gene_positions. 
# this is convienient when using gene_positions to get correlations for all genes
get_counts<-function(gene_pos, bed=bed_file) {
  stopifnot(length(gene_pos) == 1)
  counts <- system(paste("tabix", bed, gene_pos), intern=TRUE) %>%
    str_split('\t')
  stopifnot(length(counts) == 1)
  as.numeric(counts[[1]][5:length(counts[[1]])])
}

cutoff <- '05'

PGR05cor <- gene_positions %>% mutate(cor_test=map(pos, function(x) my_cor_test(safely(get_counts)(x)$result, pg_scores[,cutoff][[1]])),
                       p=map_dbl(cor_test, 'p.value'), r=map_dbl(cor_test, 'estimate'),
                       fdr=p.adjust(p, method='BH'),
                       p.adj=p.adjust(p, method='Bonforoni')
                       ) %>% 
  dplyr::select(-cor_test) %>%
  filter(!is.na(r))

PGR05cor <- right_join(genes, PGR05cor, by=c('gene_id' = 'ID')) %>% arrange(p.adj)

mutate(PGR05cor, sig_cor=ifelse(p.adj > 0.05, 'ns', ifelse(r>0, '+', '-'))) %>%
  group_by(gene_type, sig_cor) %>% summarise(n=n()) %>% spread(sig_cor, n) %>% 
  filter(!is.na(`-`) | !is.na(`+`)) %>% mutate(`% -` = `-`/ns*100, `% +` = `+`/ns*100)
```

```{r}
ENSG00000233913cor <- tibble()
for (cutoff in colnames(pg_scores)[-1]) {
  ENSG00000233913cor <- filter(gene_positions, ID=='ENSG00000233913') %>% 
    mutate(cor_test=map(pos, function(x) my_cor_test(safely(get_counts)(x)$result, pg_scores[,cutoff][[1]])),
           p=map_dbl(cor_test, 'p.value'), r=map_dbl(cor_test, 'estimate'),
           name=cutoff) %>% 
    dplyr::select(-cor_test) %>%
    bind_rows(PGRcor)
}

bonferroni <- .05/nrow(gene_positions)
ENSG00000233913cor %>%
  left_join(cut_off_mapping) %>%
  ggplot(aes(x=log10(Cutoff), y=-log10(p)))+geom_line()+geom_point()+scale_x_reverse()+ggtitle('ENSG00000233913')+geom_hline(yintercept=-log10(bonferroni), linetype=3)
```

```{r}
for (cutoff in colnames(pg_scores)[-1]) {
  print(tibble(ENSG00000233913=get_counts(filter(gene_positions, ID=='ENSG00000233913')$pos), PRS=pg_scores[,cutoff][[1]]) %>% ggplot(aes(ENSG00000233913, PRS))+geom_point()+ggtitle(cutoff))
}
```


