---
title: "Figures"
author: "Heath O'Brien"
date: "4/9/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_knit$set(fig.width=12, fig.height=8, fig.path='Figs/',
                      echo=FALSE, 
                      warning=FALSE, 
                      message=FALSE)

library(tidyverse)
library(stringr)
library(gridExtra)
library(clusterProfiler)
library(xlsx)
source("../Shiny/GENEX-FB1/FormatGGplot.R")

fittedBias <- read_delim("../Shiny/GENEX-FB1/Data/fitted.txt", "\t", escape_double = FALSE, trim_ws = TRUE) %>%
  dplyr::rename(log2FoldDiff = log2FoldChange) %>%
  mutate(Sex = ifelse(log2FoldDiff < 0, 'F', 'M'),
         ChrType = ifelse(Chr %in% c('chrX','chrY'), Chr, 'autosome'), 
         Chr = parse_factor(Chr, str_c('chr', c(seq(1,22), 'X', 'Y')))) 

fittedBias_tr <- read_delim("../Shiny/GENEX-FB1/Data/fitted_tr.txt", "\t", escape_double = FALSE, trim_ws = TRUE) %>%
  dplyr::rename(log2FoldDiff = log2FoldChange) %>%
  mutate(Sex = ifelse(log2FoldDiff < 0, 'F', 'M'),
         ChrType = ifelse(Chr %in% c('chrX','chrY'), Chr, 'autosome'), 
         Chr = parse_factor(Chr, str_c('chr', c(seq(1,22), 'X', 'Y')))) 


gene_sets <-read_delim("../Data/GeneSets.txt", 
                         "\t", escape_double = FALSE, col_names=c('gene_name', 'set', 'reference', 'Id'), 
                         trim_ws = TRUE)

target <- read_delim("../Data/SampleInfo.txt", "\t", escape_double = FALSE, trim_ws = TRUE) %>%
  mutate(label=as.character(Sample))

PlotFC <- function(genes, title) {
  plot <- ggplot(genes, aes(x=ageBin, y=log2FoldDiff, group=Id)) +
    geom_line(alpha=.1) +
    geom_point(colour='red', size=1, alpha=.25, data=filter(genes, padj<0.1)) +
    figure_theme() +
    ylab("<--- Female-biased        Male-biased --->") +
    xlab("Post-conception week") +
    theme(axis.title.y=element_text(size=9)) +
    ggtitle(title)
  plot        
}
```


Figure 1. a) Number of genes exhibiting sex-biased expression at FDR < 0.1 at each developmental time-point. b) Mean Log2-fold sex differences in all detected genes at each developmental time-point. Black dots indicate significant sex biases (FDR < 0.1). Multiple genes on the Y-chromosome are expressed in males across all time-points; the X-chromosome gene displaying pronounced differences across all time-points is XIST. Numbers of males (M) and females (F) included at each time-point are: 12 PCW = 10 M and 6 F; 13 PCW = 17 M and 14 F; 14 PCW = 8 M and 10 F; 15–16 PCW = 15 M and 8 F; 17-19 PCW = 12 M and 8 F.

```{r}
Fig1a <- fittedBias %>% filter(padj < .1 ) %>%
  ggplot(aes(x=Sex, fill=ChrType)) + geom_bar(position='stack') + 
  facet_grid(. ~ ageBin) +
    figure_theme() +
    #scale_y_continuous(breaks=seq(100,1000,100)) +
    scale_fill_manual(values=brewer.pal(6, "Set1")[c(1,2,4)]) +
    theme(strip.switch.pad.grid = unit(10, 'cm')) +
    ylab('Number sex-biased genes (FDR<0.1)') +
    xlab('Fetal sex') +
    theme(axis.title.y=element_text(size=9)) +
    theme(axis.title.x=element_text(size=9)) +
    ggtitle('A.')

Fig1b <- ggplot(fittedBias, aes(x=ageBin, y=log2FoldDiff, group=Id)) + 
    geom_line(alpha=1, aes(colour=ChrType)) +
    geom_point(colour='black', size=1, alpha=.25, data=filter(fittedBias, padj < .1 )) +
    scale_colour_manual(values=brewer.pal(6, "Set1")[c(1,2,4)]) + 
    figure_theme() +
    ylab("<--- Female-biased        Male-biased --->") +
    xlab("Post-conception week") +
    theme(axis.title.y=element_text(size=9)) +
    theme(axis.title.x=element_text(size=9)) +
    ggtitle('B.') +
    theme(legend.position='right')


png(file="Figures/Fig1.png", bg="transparent", width=183, height=70, units='mm', res=300)
grid.arrange(Fig1a, Fig1b, ncol=2, widths=c(1,2))
dev.off()
pdf(file="Figures/Fig1.pdf", 7.2, 3)
grid.arrange(Fig1a, Fig1b, ncol=2, widths=c(1,2))
dev.off()

grid.arrange(Fig1a, Fig1b, ncol=2, widths=c(1,2))

```

Figure 2: Log2 fold sex differences across time-points for (a) replicating fetal genes and b) adult neuron genes. Red dots indicate significant sex bias in expression (FDR < 0.1)
``` {r}
AN <- gene_sets %>% 
  filter(set=='cluster7' & gene_name != 'XIST') %>% 
  inner_join(fittedBias)

group_by(AN, ageBin) %>% summarise(n=n())
FR <- gene_sets %>% 
  filter(set=='cluster9' & gene_name != 'RPS4Y1') %>%
  inner_join(fittedBias)
group_by(FR, ageBin) %>% summarise(n=n())
png(file="Figures/Fig2.png", bg="transparent", width=183, 
    height=70, units='mm', res=300)
grid.arrange(PlotFC(FR, 'A.'), PlotFC(AN, 'B.'), ncol=2)
dev.off()
pdf(file="Figures/Fig2.pdf", 7.2, 3)
grid.arrange(PlotFC(FR, 'A.'), PlotFC(AN, 'B.'), ncol=2)
dev.off()

grid.arrange(PlotFC(FR, 'A.'), PlotFC(AN, 'B.'), ncol=2)

```

Figure 3: Expression data for selected genes characteristic of mature neurons (GABRA1, GRIN2A) and proliferating neural progenitor cells (NES, EOMES) in 14 PCW brain samples (8 male, 10 female).
```{r}
PlotTimepoint<-function(geneID, counts, fittedBias, target, ages, title) {
  geneID = str_replace(geneID, '(ENSG\\d+)\\.\\d+', '\\1')
  ageSplit <- strsplit(ages, '-')[[1]]
  min <- ageSplit[1]
  max <- ageSplit[length(ageSplit)]
  data <- counts %>% filter(SYMBOL == geneID | Id == geneID) %>%  
    dplyr::select(-SYMBOL, -Id, -Chr) %>%
    gather() %>%
    separate(key, into=c('norm', 'label'), sep='[.]') %>%
    dplyr::select(label, value) %>%
    left_join(target) %>%
    filter(PCW >= min & PCW <= max)
  mean <- filter(fittedBias, SYMBOL == geneID | Id == geneID) %>% filter(ageBin==ages)
  fc <- mean$log2FoldDiff[1] %>% format(digits=2)
  pval <- mean$pvalue[1]
  qval <- mean$padj[1]
  mean <- mean %>% dplyr::select(Male, Female) %>%
    gather('Sex', 'mean')
  plot<-  ggplot(data, aes(x=Sex, colour=Sex)) + 
    geom_jitter(aes(y=value), height = 0, width=.1, alpha=.75) + 
    geom_errorbar(aes(ymin=mean, ymax=mean), colour='black', size=1, width=.5, data=mean) +
    ylab("Normalised counts") +
    xlab('') +
    figure_theme() +
    scale_colour_brewer(type = "qual", palette = 6) +
     theme(plot.title=element_text(face="italic")) +
    ggtitle(title) 
  plot
}

Fig3a <- PlotTimepoint('GABRA1', counts, fittedBias, target, '14', 'GABRA1')
Fig3b <- PlotTimepoint('GRIN2A', counts, fittedBias, target, '14', 'GRIN2A')
Fig3c <- PlotTimepoint('NES', counts, fittedBias, target, '14', 'NES')
Fig3d <- PlotTimepoint('EOMES', counts, fittedBias, target, '14', 'EOMES')
png(file="Figures/Fig3.png", bg="transparent", width=183, height=140, units='mm', res=300)
grid.arrange(Fig3a, Fig3b, Fig3c, Fig3d, ncol=2)
dev.off()
pdf(file="Figures/Fig3.pdf", 7.2, 5.5)
grid.arrange(Fig3a, Fig3b, Fig3c, Fig3d, ncol=2)
dev.off()

grid.arrange(Fig3a, Fig3b, Fig3c, Fig3d, ncol=2)
```

Figure S1

```{r}
p1 <- ggplot(target, aes(x=PCW, fill=Sex)) +
  geom_bar() +
  facet_grid(Sex ~ .) +
  scale_y_continuous(breaks=seq(0,100, 2)) +
  scale_x_continuous(breaks=seq(11,19, 1)) +
  figure_theme() +
  xlab("Post-conception weeks") +
  ylab("Count") +
  theme(axis.text.x=element_text(size=8)) +
  scale_fill_brewer(type = "qual", palette = 6) +
  ggtitle('A.')

target <- mutate(target, age_bin =ifelse(target$PCW == 16, 15, 
                                     ifelse(target$PCW > 16, 16, target$PCW)))
p2 <- ggplot(target, aes(x=age_bin, fill=Sex)) +
  geom_bar() +
  facet_grid(Sex ~ .) +
  scale_y_continuous(breaks=seq(0,100, 2)) +
  scale_x_continuous(breaks=c(11,12,13,14,15,16),
                     labels=c('11','12','13','14','15-16','17-19')) +
  figure_theme() +
  xlab("Post-conception weeks") +
  ylab("Count") +
  theme(axis.text.x=element_text(size=8)) +
  scale_fill_brewer(type = "qual", palette = 6) +
  ggtitle('B.')

pdf(file="Figures/FigS1.pdf", 7.2, 5.5)
grid.arrange(p1, p2, ncol=2)
dev.off()
png(file="Figures/FigS1.png", bg="transparent", width=183, height=140, units='mm', res=300)
grid.arrange(p1, p2, ncol=2)
dev.off()
grid.arrange(p1, p2, ncol=2)

```

Figure S2
```{r}
Neuronal <- gene_sets %>% 
  filter(set=='Neuronal' & gene_name != 'XIST') %>% 
  inner_join(fittedBias)
group_by(Neuronal, ageBin) %>% summarise(n=n())

RG <- gene_sets %>% 
  filter(set=='RadialGlia' & gene_name != 'XIST') %>%
  inner_join(fittedBias)
group_by(RG, ageBin) %>% summarise(n=n())

NPC <- gene_sets %>% 
  filter(set=='NPC' & gene_name != 'RPS4Y1') %>%
  inner_join(fittedBias)
group_by(NPC, ageBin) %>% summarise(n=n())

png(file="Figures/FigS2.png", bg="transparent", width=183, 
    height=210, units='mm', res=300)
grid.arrange(PlotFC(NPC, 'A. iPSC-derived neural progenitor cell genes'),
             PlotFC(RG, 'B. Radial glia genes'),
             PlotFC(Neuronal, 'C. Fetal neuron genes'), 
             ncol=1)
dev.off()
pdf(file="Figures/FigS2.pdf", 7.2, 9)
grid.arrange(PlotFC(NPC, 'A. iPSC-derived neural progenitor cell genes'),
             PlotFC(RG, 'B. Radial glia genes'),
             PlotFC(Neuronal, 'C. Fetal neuron genes'), 
             ncol=1)
dev.off()

grid.arrange(PlotFC(NPC, 'A. iPSC-derived neural progenitor cell genes'),
             PlotFC(RG, 'B. Radial glia genes'),
             PlotFC(Neuronal, 'C. Fetal neuron genes'), 
             ncol=1)

```

Enrichment Analysis
Week 14
```{r}

#disease2gene <- filter(gene_sets, ! set %in% c('SandersASD', 'SFARI'))[, c("set", "gene_name")] 
disease2gene <- filter(gene_sets, ! set %in% c('SandersASD', 'SFARI')) %>% dplyr::select(set, gene_name) 
FemaleDEG <- fittedBias %>% filter(ageBin == '14' & padj<0.1 & log2FoldDiff <0)

FemaleEnrichment <- summary(enricher(FemaleDEG$SYMBOL, TERM2GENE=disease2gene, pAdjustMethod='bonferroni'))
FemaleEnrichment$Direction <- 'FemaleBiased'

MaleDEG <- fittedBias %>% filter(ageBin == '14' & padj<0.1 & log2FoldDiff >0)

MaleEnrichment <- summary(enricher(MaleDEG$SYMBOL, TERM2GENE=disease2gene, pAdjustMethod='bonferroni'))
MaleEnrichment$Direction <- 'MaleBiased'
Enrichment <- bind_rows(FemaleEnrichment, MaleEnrichment) %>% 
  separate(GeneRatio, c('x1', 'y1'), sep='/', remove=FALSE) %>% 
  separate(BgRatio, c('x2', 'y2'), sep='/', remove=FALSE) %>%
  mutate(Enrichment=(as.numeric(x1)/as.numeric(y1))/(as.numeric(x2)/as.numeric(y2))) %>%
  dplyr::select(Direction, ID, GeneRatio, BgRatio, Enrichment, pvalue, p.adjust, qvalue, geneID)

#Need to correct for 10 test because we tested 2 sets of DE genes
#For some mysterious reason, enricher is correcting for 4 tests even though there are clearly 5 gene sets being tested.
Enrichment$p.adjust <- p.adjust(Enrichment$pvalue, method='bonferroni', n=10)

write_tsv(Enrichment, "Tables/Enrichment14.txt")
Enrichment
```

## All weeks (65 high-cofindence Autism genes and 79 high confidence X-linked ID genes)
- Sanders et al 2015, Piton et al 2013
```{r}

disease2gene <- bind_rowsfilter(gene_sets, set %in% c('SandersASD', 'PitonID'))[, c("set", "gene_name")]

FemaleDEG <- fittedBiasAll %>% filter(padj<0.1 & log2FoldDiff < 0)

FemaleEnrichment <- summary(enricher(FemaleDEG$SYMBOL, TERM2GENE=disease2gene, pAdjustMethod='bonferroni'))
dim(FemaleEnrichment)
#FemaleEnrichment$Direction <- 'FemaleBiased'

MaleDEG <- fittedBiasAll %>% filter(padj<0.1 & log2FoldDiff > 0)

MaleEnrichment <- summary(enricher(MaleDEG$SYMBOL, TERM2GENE=disease2gene, pAdjustMethod='bonferroni'))
MaleEnrichment$Direction <- 'MaleBiased'
Enrichment <- bind_rows(FemaleEnrichment, MaleEnrichment) %>% 
  separate(GeneRatio, c('x1', 'y1'), sep='/', remove=FALSE) %>% 
  separate(BgRatio, c('x2', 'y2'), sep='/', remove=FALSE) %>%
  mutate(Enrichment=(as.numeric(x1)/as.numeric(y1))/(as.numeric(x2)/as.numeric(y2))) %>%
  dplyr::select(Direction, ID, GeneRatio, BgRatio, Enrichment, pvalue, p.adjust, qvalue, geneID)

#Need to correct for test because 2 sets of DE genes
Enrichment$p.adjust <- p.adjust(Enrichment$pvalue, method='bonferroni', n=2)
write_tsv(Enrichment, "Tables/EnrichmentAll.txt")
Enrichment
```

Supplementary Table 1
```{r}
DEG12_19 <- fittedBias %>% filter(padj<0.1) %>%
  mutate(`FoldDiff` = 2^log2FoldDiff, 
         pvalue = as.numeric(format(pvalue, digits=2)), 
         padj = as.numeric(format(padj, digits=2))) %>%
  arrange(Chr) %>%
  dplyr::select(`Ensembl Gene ID` = Id, 
         `Gene ID` = SYMBOL,
         Chromosome = Chr,
         `Mean Count Male` = Male, 
         `Mean Count Female` = Female,
         `Fold Difference (M/F)` = FoldDiff,
         `p value` = pvalue,
         `FDR` = padj)

write.xlsx2(as.data.frame(DEG12_19), 
            file="../Tables/SupplementalTables.xlsx", 
            row.names=FALSE,
            sheetName='TblS1')
```

Supplementary Table 2
```{r}
DEG12_19_tr <- fittedBias_tr %>% filter(padj<0.1) %>%
  mutate(`FoldDiff` = 2^log2FoldDiff, 
         pvalue = as.numeric(format(pvalue, digits=2)), 
         padj = as.numeric(format(padj, digits=2))) %>%
  arrange(Chr) %>%
  dplyr::select(`Ensembl Transcript ID` = Id,
         `Ensembl Gene ID` = GeneId,
         `Gene ID` = SYMBOL,
         Chromosome = Chr,
         `Mean Count Male` = Male, 
         `Mean Count Female` = Female,
         `Fold Difference (M/F)` = FoldDiff,
         `p value` = pvalue,
         `FDR` = padj)

write.xlsx2(as.data.frame(DEG12_19_tr), 
            file="../Tables/SupplementalTables.xlsx", 
            row.names=FALSE,
            sheetName='TblS2',
            append=TRUE)
```

# Supplementary Table 3
- there are several issue with this table:
    - XIST is not included as a DE gene with the gene-level analysis because it was not tested. It is in the background, so it must be because it had samples with high Cooks distance
    - this illustrates an additional problem with the web app: genes where padj is NA are not included no matter what the slider is set to, so using the gene set downloaded from there as the background misses expressed genes that are affected by outlier samples.
    - There is a DE gene in these lists that does not show up in the web app because it can't be associated to any Ensembl gene. It's probably best to screen these out, since we can't really say anything about them anyway.
    - Because this analysis filters by padj before rounding while the web app filters after, there is one gene with and FDR of 0.099 which is included in these tables but not the web app.
    - I used table S10 from the Mele paper (Genes differentially expressed between males and females (FDR <0.05)). There's also S13 (Genes differentially expressed between males and females within each tissue (FDR<0.05)), which is dominate by the breast. I haven't had a chance to looks through the paper and figure out exactly what fig S10 is.
```{r}
previous <- read_tsv("../Data/previous_findings.txt")
sig_res <- fittedBias %>%
  filter(padj < 0.1) %>%
  mutate(result = paste0(format(log2FoldDiff, digits=2), ' (', format(padj, digits=2), ')'),
         level = 'Gene-level Analysis') %>%
  dplyr::select(Id, SYMBOL, Chr, result, level)

sig_res_tr <- fittedBias_tr %>%
  arrange(padj) %>%
  group_by(GeneId) %>%
  dplyr::slice(1) %>%
  filter(padj < 0.1) %>%
  dplyr::select(-Id, Id=GeneId) %>%
  mutate(result = paste0(format(log2FoldDiff, digits=2), ' (', format(padj, digits=2), ')'),
         level = 'Transcript-level Analysis') %>%
  dplyr::select(Id, SYMBOL, Chr, result, level)

sig_res_all <- bind_rows(sig_res, sig_res_tr) %>%
  spread(level, result) %>% 
  arrange(Chr) %>% 
  dplyr::rename(`Ensembl ID` = Id, 
                `Gene ID` = SYMBOL,
                Chromosome = Chr) %>%
  left_join(previous)

write.xlsx2(as.data.frame(sig_res_all), 
            file="../Tables/SupplementalTables.xlsx", 
            row.names=FALSE,
            sheetName='TblS3',
            append=TRUE)
```

Supplementary Table 3
```{r}
Xinactivation <- read_tsv('Data/Xinactivation.txt')
write.xlsx2(as.data.frame(Xinactivation), 
            file="Tables/SupplemtalTables.xlsx", 
            row.names=FALSE,
            sheetName='TblS3',
            append=TRUE)
```

Supplementary Tables 4 & 5
```{r}
GO_M_all <- read_tsv('Data/DAVID_M12_19.txt')
write.xlsx2(as.data.frame(GO_M_all), 
            file="Tables/SupplemtalTables.xlsx", 
            row.names=FALSE,
            sheetName='TblS4',
            append=TRUE)

GO_F_all <- read_tsv('Data/DAVID_F12_19.txt')
write.xlsx2(as.data.frame(GO_F_all), 
            file="Tables/SupplemtalTables.xlsx", 
            row.names=FALSE,
            sheetName='TblS5',
            append=TRUE)

```

Supplementary Tables 6 - 10
```{r}
DEG12 <- fittedBias %>% filter(padj<0.1 & ageBin == 12) %>%
  mutate(`FoldDiff` = 2^log2FoldDiff, 
         pvalue = as.numeric(format(pvalue, digits=2)), 
         padj = as.numeric(format(padj, digits=2))) %>%
  arrange(Chr) %>%
  dplyr::select(`Ensembl ID` = Id, 
         `Gene ID` = SYMBOL,
         Chromosome = Chr,
         `Mean Count Male` = Male, 
         `Mean Count Female` = Female,
         `Fold Difference (M/F)` = FoldDiff,
         `p value` = pvalue,
         `FDR` = padj)

write.xlsx2(as.data.frame(DEG12), 
            file="Tables/SupplemtalTables.xlsx", 
            row.names=FALSE,
            sheetName='TblS6',
            append=TRUE)

DEG13 <- fittedBias %>% filter(padj<0.1 & ageBin == 13) %>%
  mutate(`FoldDiff` = 2^log2FoldDiff, 
         pvalue = as.numeric(format(pvalue, digits=2)), 
         padj = as.numeric(format(padj, digits=2))) %>%
  arrange(Chr) %>%
  dplyr::select(`Ensembl ID` = Id, 
         `Gene ID` = SYMBOL,
         Chromosome = Chr,
         `Mean Count Male` = Male, 
         `Mean Count Female` = Female,
         `Fold Difference (M/F)` = FoldDiff,
         `p value` = pvalue,
         `FDR` = padj) 

write.xlsx2(as.data.frame(DEG13), 
            file="Tables/SupplemtalTables.xlsx", 
            row.names=FALSE,
            sheetName='TblS7',
            append=TRUE)

DEG14 <- fittedBias %>% filter(padj<0.1 & ageBin == 14) %>%
  mutate(`FoldDiff` = 2^log2FoldDiff, 
         pvalue = as.numeric(format(pvalue, digits=2)), 
         padj = as.numeric(format(padj, digits=2))) %>%
  arrange(Chr) %>%
  dplyr::select(`Ensembl ID` = Id, 
         `Gene ID` = SYMBOL,
         Chromosome = Chr,
         `Mean Count Male` = Male, 
         `Mean Count Female` = Female,
         `Fold Difference (M/F)` = FoldDiff,
         `p value` = pvalue,
         `FDR` = padj)

write.xlsx2(as.data.frame(DEG14), 
            file="Tables/SupplemtalTables.xlsx", 
            row.names=FALSE,
            sheetName='TblS8',
            append=TRUE)

DEG15_16 <- fittedBias %>% filter(padj<0.1 & ageBin == '15-16') %>%
  mutate(`FoldDiff` = 2^log2FoldDiff, 
         pvalue = as.numeric(format(pvalue, digits=2)), 
         padj = as.numeric(format(padj, digits=2))) %>%
  arrange(Chr) %>%
  dplyr::select(`Ensembl ID` = Id, 
         `Gene ID` = SYMBOL,
         Chromosome = Chr,
         `Mean Count Male` = Male, 
         `Mean Count Female` = Female,
         `Fold Difference (M/F)` = FoldDiff,
         `p value` = pvalue,
         `FDR` = padj)

write.xlsx2(as.data.frame(DEG15_16), 
            file="Tables/SupplemtalTables.xlsx", 
            row.names=FALSE,
            sheetName='TblS9',
            append=TRUE)

DEG17_19 <- fittedBias %>% filter(padj<0.1 & ageBin == '17-19') %>%
  mutate(`FoldDiff` = 2^log2FoldDiff, 
         pvalue = as.numeric(format(pvalue, digits=2)), 
         padj = as.numeric(format(padj, digits=2))) %>%
  arrange(Chr) %>%
  dplyr::select(`Ensembl ID` = Id, 
         `Gene ID` = SYMBOL,
         Chromosome = Chr,
         `Mean Count Male` = Male, 
         `Mean Count Female` = Female,
         `Fold Difference (M/F)` = FoldDiff,
         `p value` = pvalue,
         `FDR` = padj)

write.xlsx2(as.data.frame(DEG17_19), 
            file="Tables/SupplemtalTables.xlsx", 
            row.names=FALSE,
            sheetName='TblS10',
            append=TRUE)
```

Supplementary Tables 11 & 12
```{r}
GO_M_14 <- read_tsv('Data/DAVID_M14.txt')
write.xlsx2(as.data.frame(GO_M_14), 
            file="Tables/SupplemtalTables.xlsx", 
            row.names=FALSE,
            sheetName='TblS11',
            append=TRUE)

GO_F_14 <- read_tsv('Data/DAVID_F14.txt')
write.xlsx2(as.data.frame(GO_F_14), 
            file="Tables/SupplemtalTables.xlsx", 
            row.names=FALSE,
            sheetName='TblS12',
            append=TRUE)

```

Supplementary Table 13
```{r}
SampleInfo <- read_tsv("Data/SampleInfo.txt") %>%
  mutate(`Total Read Pairs (millions)` = round(TotalFragments/1000000)) %>%
  dplyr::select(-TotalFragments)
write.xlsx2(as.data.frame(SampleInfo), 
            file="Tables/SupplemtalTables.xlsx", 
            row.names=FALSE,
            sheetName='TblS13',
            append=TRUE)

```
